Halo alignments with large scale tidal and velocity fields

### 2013-02-24 paper/main.tex
all new plots integrated

\title[Vweb \& Tweb]{Halo alignments with large scale tidal and velocity fields}
\author[J.E. Forero-Romero and M. Dijkstra]{
\parbox[t]{\textwidth}{\raggedright 
  A.A.$^{1}$ 
  B.B.$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

\subsection{Shape Alignment}
\begin{figure}
\includegraphics[width=0.50\textwidth]{../plots/JT256.ps}
\caption{
}
\label{fig:JT256}
\end{figure}

\subsection{Angular Momentum Alignment}

@@

>>>>

\title[Vweb \& Tweb]{Halo alignments with large scale tidal and velocity fields}
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Sergio Contreras$^{1}$ 
  Jaime E. Forero-Romero$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T1V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T2V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/256/256_T3V3.ps}
\caption{Interweb alignment for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T1V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T2V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/512/512_T3V3.ps}
\caption{Interweb alignment for $512^3$ grid resolution.}
\end{figure*}

\subsection{Shape Alignment}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_V3.ps}
\caption{Shape alignment for the vweb at $256^3$ resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/256_AX1_T3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/256_AX2_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/256_AX3_T3.ps}
\caption{Shape alignment for the tweb at $256^3$ resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_V3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_V3.ps}
\caption{Shape alignment for the vweb at $512^3$ resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax1_VT/512_AX1_T3.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax2_VT/512_AX2_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Ax3_VT/512_AX3_T3.ps}
\caption{Shape alignment for the tweb at $512^3$ resolution.}
\end{figure*}

\newpage
\subsection{Angular Momentum Alignment}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_V3.ps}
\caption{Angular momentum alignment with the Vweb for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_V3.ps}
\caption{Angular momentum alignment with the Vweb for $512^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/256_J_T3.ps}
\caption{Angular momentum alignment with the Tweb for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_V3.ps}
\caption{Peculiar velocity alignment with the Vweb for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_V3.ps}
\caption{Peculiar velocity alignment with the Vweb for $512^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/256_vel_T3.ps}
\caption{Peculiar velocity alignment with the Tweb for $256^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}
